\documentclass[letterpaper,11pt]{article}
%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
\usepackage{tcolorbox}
%\usepackage{fullpage}
%\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\definecolor{yeetGreen}{HTML}{C1FFC4}
\newtcolorbox{trixiematel}[1][]
{
    colframe=blue!50!black, colback=lightgray,
  #1,
}
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{ \begin{trixiematel}\textbf{#1}\end{trixiematel}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
                \textbf{#1} & #2 \\
                \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{2pt}}
\newcommand{\Heading}[5]{
    \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
        \textbf{\Large #1}  & #2\\
        #3 & #4 \\
        & #5 \\
        \end{tabular*}}
%-----------------------------------------------------------

\begin{document}\Heading{Troy Wiegand}{+15742708328}{troy@troywiegand.com}{troywiegand.com}{github.com/troywiegand}
\resheading{Education}
\begin{description}
\item
\ressubheading{Butler University}{Indianapolis, IN}{B.S. Mathematics and Computer Science}{August 2016 - Present} 


Relevant Courses: Parallel Algorithms, Object Oriented Design, Algorithms, Teaching Practicum, Elementary Statistics, Algebra: Groups, Real Analysis 1, EPICS, Databases, Computer Organization, Object-Oriented Programming, Discrete 2, Real Analysis 2, Complex Analysis, Discrete Mathematics, Differential Equations, Numerical Analysis, Basics of Advanced Mathematics, Calculus 3, Linear Algebra, Calculus 2, Intro to CS

\end{description}
\resheading{Work Experience}
\begin{description}
\item
\ressubheading{Computer Science Department}{Butler University}{Tutor}{August 2018 - Present} 


Ran an open Computer Science tutor session for Butlers introductory coding course taught using C++ and introductory Discrete Mathematics course.  This runs two hours once a week.  Balancedmultiple projects to give the best advice and extra educational support to help all of the differentstudents I work with.

\item
\ressubheading{Mathematics Department}{Butler University}{Tutor}{August 2017 - Present} 


Ran an open tutoring session for all 100 and 200 level Math Courses.

\item
\ressubheading{Mathematics Department}{Butler University}{Intern}{January 2017 - Present} 


I work with professors to help create and administer learning assessments and activities. I hold my own independent office hours were students of my classes could come ask for assistance. I run review sessions for my classes and during finals week a review session for every section of the courses I enriched. I have worked with Pre-Calculus, Calculus I, Calculus II, and Linear Algebra students.

\item
\ressubheading{Ace Hardware}{Winamac, IN}{Manager}{June 2010 - Present} 


I coordinated inventory management. I communicated and delegated tasks to coworkers. I installed and maintained various technologies such as new computers for registers, new signature pads, and telecommunication infrastructure.


 \end{description}

\resheading{Miscellaneous Experience}
\begin{description}
\item
\ressubheading{Indiana Association of Student Councils}{Indiana}{Technology Head}{April 2019 - Present} 


Help Mantain and Develop Necessary Technology Solutions such as the IASC website, conference audio/video setup, and various promotional videos. Helped Soggy Sam survive lfe.

\end{description}\resheading{Skills}

\begin{description}
\item[Languages:]
C++, Java, JavaScript, HTML, CSS, Bash, Python, C\#, \LaTeX, React, SQL\end{description}\end{document}